Challenges to transboundary fisheries management in North America under climate change

### 2019-11-04 Ecol_Manuscript_Draft.Rmd
Inlcuded the here package for knitting to the thesis

---
title: "Challenges to transboundary fisheries management in North America under climate change"
author: "Juliano Palacios-Abrantes^1^ U. Rashid Sumaila^1^ William W. L. Cheung^1^"
subtitle: "[THIRD DRAFT]"
date: "^1^ Institute for the Oceans and Fisheries, University of British Columbia, Vancouver, Canada"
output:
  word_document: default
  pdf_document: default
bibliography: Ecol_Analysis/Oceans_Canada_Biblio.bib
editor_options: 
  chunk_output_type: console
csl: Ecol_Analysis/harvard.csl
---

```{r setup, eval=T, echo=F, warning=F,message=F, results='hide'}

@@

#### Library ####
packages <- c(
  "readxl", # Read dataframe
  "dplyr", # Data manipulation
  "tidyr", # Data manipulation
  "ggplot2", #Nice grpahs and spatial analysis
  "RColorBrewer",
  "data.table",
  "ggrepel",
  "sf",
  # "sp",
  # "rgdal", #Spatial analysis 
  "tools"#, #Spatial analysis 
  # "png", # For reading plots in chunk codes
  # "grid" # For reading plots in chunk codes
)

@@

![Fig 1. Map of North America with the regulatory areas of the IPHC and the NAFO sub-region related to the Gulf of Main agreement](./Figures/Ecol//Fig1.png)

@@

```{r Load_Data, echo = F, eval = T, results='hide', warning=F,message=F}

@@

#Data provided by Vicki Lam
EEZIDs_List <- read_excel("./Data/Spatial/Updated_EEZList_17June2016.xlsx")
EEZ_CellID <- read_excel("./Data/Spatial/EEZ_CellID.xlsx")
colnames(EEZ_CellID) <- c("EEZID","INDEX")

# From (/Users/jpalacios/Documents/UBC/Oceans_Project/Distribution/By Cell/By_Cell_Analysis.Rmd)
Raw_DBEM_Results <- data.table::fread("./Data/Distribution/Raw_Data.csv") %>% 
  filter(Species != "Anoplopoma fimbria") #Remove

@@

```{r Changes_Data_All, eval =T, echo = F, fig.height=8, fig.width=12}

@@

![Fig 2. Percentage change of MCP of transboundary fisheries of North America for mid century (2046-2055) referent to 2005-2014 under a A) low emission scenario and; B) high emission scenario.](./Figures/Ecol/Fig2.png)

@@

```{r Figure_3, eval = F, echo =F, fig.cap="Percentage Change of MCP for Species managed by the IPHC. A, RCP 2.6 represents a low emission scenario (high mitigation). B, RCP 8.5 represents a high emission scenario (status quo)"}

img <- readPNG("/Users/jpalacios/Documents/UBC/Oceans_Project/Manuscript/Results/Fig3.png")
grid.raster(img)

@@

![Fig 3. Percentage change of MCP for species managed by the IPHC for mid century (2046-2055) referent to 2005-2014 under a A) low emission scenario and B) high emission scenario.](./Figures/Ecol/Fig3.png)

@@

```{r Figure_4, eval = T, echo =F, fig.cap="Percentage change of stock-share ratio for IPHC under two RCPs for Mid century (2046-2055)"}

Fig4 <- readPNG("~/Documents/UBC/Oceans_Project/Manuscript/Results/Fig4.png")
grid.raster(Fig4)

@@

![Fig 4. Percentage change of stock-share ratio for IPHC under A) low emission scenario and B) high emission scenario for mid century (2046-2055) referent to 2005-2014.](./Figures/Ecol/Fig4.png)

@@

Fig4 <- readPNG("./Figures/Ecol/Fig5.png")
grid.raster(Fig5)

@@

![Fig 5. Percentage change of MCP in the Gulf of Main under, A) low emission scenario; and B) high emission for mid century (2041-2060) referent to present (2005-2014)](./Figures/Ecol/Fig5.png)

@@

Fig4 <- readPNG("./Figures/Ecol/Fig6.png")
grid.raster(Fig5)

@@

![Fig 6. Changes in MCP stock-share ratio for Gulf of Main under (A) low emission scenario; and (B) high emission for mid century (2041-2060) referent to 2005-2014](./Figures/Ecol/Fig6.png)

@@

```{r Functions, eval = F}

@@

```{r Old analysis, eval = F}

>>>>

---
title: "Challenges to transboundary fisheries management in North America under climate change"
author: "Juliano Palacios-Abrantes^1^ U. Rashid Sumaila^1^ William W. L. Cheung^1^"
subtitle: "[THIRD DRAFT]"
date: "^1^ Institute for the Oceans and Fisheries, University of British Columbia, Vancouver, Canada"
output:
  # word_document: default
  pdf_document: default
bibliography: Ecol_Analysis/Oceans_Canada_Biblio.bib
editor_options: 
  chunk_output_type: console
csl: Ecol_Analysis/harvard.csl
---

```{r Ch3_setup, eval = T, echo=F, warning=F,message=F, results='hide'}

@@

#### Library ####
packages <- c(
  "here", # For all thesis
  "readxl", # Read dataframe
  "dplyr", # Data manipulation
  "tidyr", # Data manipulation
  "ggplot2", #Nice grpahs and spatial analysis
  "RColorBrewer",
  "data.table",
  "ggrepel",
  "sf",
  "knitr", # Nice tables
  "kableExtra", # Nice tables
  # "sp",
  # "rgdal", #Spatial analysis 
  "tools", #Spatial analysis 
  "png", # For reading plots in chunk codes
  "grid" # For reading plots in chunk codes
)

@@

```{r Figure_1, eval = T, echo =F, fig.cap="Map of North America with the regulatory areas of the IPHC and the NAFO sub-region related to the Gulf of Main agreement"}

img <- readPNG(here("Figures/Ecol/Fig1.png"))
grid.raster(img)

<!-- ![Fig 1. Map of North America with the regulatory areas of the IPHC and the NAFO sub-region related to the Gulf of Main agreement](./Figures/Ecol//Fig1.png) -->

@@

```{r Load_Data, echo = F, eval = F, results='hide', warning=F,message=F}

@@

#Data provided by Vicki Lam
EEZIDs_List <- read_excel(here("Data/Spatial/Updated_EEZList_17June2016.xlsx"))
EEZ_CellID <- read_excel(here("Data/Spatial/EEZ_CellID.xlsx"))
colnames(EEZ_CellID) <- c("EEZID","INDEX")

# DBEM Coordinate system
Coor <- fread(here("Data/Spatial/Lon_Lat_DBEM.txt"),header = FALSE)
colnames(Coor) <- c("INDEX","Longitude","Latitude")

# From (/Users/jpalacios/Documents/UBC/Oceans_Project/Distribution/By Cell/By_Cell_Analysis.Rmd)
Raw_DBEM_Results <- data.table::fread(here("Data/Distribution/Raw_Data.csv")) %>% 
  filter(Species != "Anoplopoma fimbria") #Remove

@@

```{r Changes_Data_All, eval = F, echo = F, fig.height=8, fig.width=12}

@@

```{r Figure_2, eval = T, echo =F, fig.cap="Percentage change of MCP of transboundary fisheries of North America for mid century (2046-2055) referent to 2005-2014 under a A) low emission scenario and; B) high emission scenario."}

img <- readPNG(here("Figures/Ecol/Fig2.png"))
grid.raster(img)

<!-- ![Fig 2. Percentage change of MCP of transboundary fisheries of North America for mid century (2046-2055) referent to 2005-2014 under a A) low emission scenario and; B) high emission scenario.](./Figures/Ecol/Fig2.png) -->

@@

```{r Figure_3, eval = T, echo =F, fig.cap="Percentage Change of MCP for Species managed by the IPHC. A, RCP 2.6 represents a low emission scenario (high mitigation). B, RCP 8.5 represents a high emission scenario (status quo)"}

img <- readPNG(here("Figures/Ecol/Fig3.png"))
grid.raster(img)

@@

<!-- ![Fig 3. Percentage change of MCP for species managed by the IPHC for mid century (2046-2055) referent to 2005-2014 under a A) low emission scenario and B) high emission scenario.](./Figures/Ecol/Fig3.png) -->

@@

```{r Figure_4, eval = T, echo =F, fig.cap="Percentage change of stock-share ratio for IPHC under A) low emission scenario and B) high emission scenario for mid century (2046-2055) referent to 2005-2014."}

Fig4 <- readPNG(here("Figures/Ecol/Fig4.png"))
grid.raster(Fig4)

@@

<!-- ![Fig 4. Percentage change of stock-share ratio for IPHC under A) low emission scenario and B) high emission scenario for mid century (2046-2055) referent to 2005-2014.](./Figures/Ecol/Fig4.png) -->

@@

Fig5 <- readPNG(here("Figures/Ecol/Fig5.png"))
grid.raster(Fig5)

@@

<!-- ![Fig 5. Percentage change of MCP in the Gulf of Main under, A) low emission scenario; and B) high emission for mid century (2041-2060) referent to present (2005-2014)](./Figures/Ecol/Fig5.png) -->

@@

Fig6 <- readPNG(here("Figures/Ecol/Fig6.png"))
grid.raster(Fig6)

@@

<!-- ![Fig 6. Changes in MCP stock-share ratio for Gulf of Main under (A) low emission scenario; and (B) high emission for mid century (2041-2060) referent to 2005-2014](./Figures/Ecol/Fig6.png) -->

@@

```{r Functions, eval = F, echo = F}

@@

```{r Old analysis, eval = T, echo = T}
